```{r, warning = FALSE, message = FALSE}
library(tidyverse) # stringr package is part of the tidyverse collection.
```


## Illustrate S3 System -- U of I Women's Basketball Team example

* Ensure you’ve read the following section before watching this video.
  + <https://adv-r.hadley.nz/s3.html#s3-classes>
* The main components of S3: **classes, generics, and methods**
* Three functions used in most classes: **constructor, helper, validator**.
* Generics, methods, and dispatch

## U of I Women's Basketball Team

<https://fightingillini.com/sports/womens-basketball/roster>

### Objective: Display the profile information according to roles

* For player, print the profile information like
  + Adalia Mckenzie is a player on the U of I Women's Basketball Team. Her jersey number is 24. Adalia is a student in her Senior year. She is 5-10 tall (177.8 cm). Her position is Guard.
* For staff, print the profile information like
  + Shauna Green is **the Head Coach** of the U of I Women's Basketball Team.
  + Maya Solomon is **a staff member** of the U of I Women's Basketball Team.
* For all other people, like the spectator, print the information like
  + Weijia Jia is neither a player nor a staff member.
  
  


## Create Player Class

### Constructor Function

```{r}
new_player = function(x){
  validate_player(x) # Validator, defined below
  structure(
    list(firstname = str_to_title(x$firstname), # str_to_title() is from stringr
         lastname = str_to_title(x$lastname), # str_to_title() converts to title case
         jersey = as.character(x$jersey),
         height_inches = x$height,
         position = str_to_title(x$position),
         studentclass = str_to_title(x$class), 
         heightcm = convertHeightToCm(x$height) # Helper function, defined below
         ),
    class = "player"
  )
}
```


### Helper Function

Convert the height from the "feet-inches" pattern to centimeters. 

```{r}
convertHeightToCm <- function(height) {
    # Split the input string by the dash
    parts <- str_split(height, "-")[[1]] # str_split() is from stringr package
    
    # Extract feet and inches as numeric values
    feet <- as.numeric(parts[1])
    inches <- as.numeric(parts[2])
    
    # Convert feet to inches and then total inches to centimeters
    height_inches <- (feet * 12) + inches
    height_cm <- height_inches * 2.54
    
    return(height_cm)
}

```

### Validator Function

* If any information is missing, print '... is missing'.
* If the pattern of height doesn't follow the "feet-inches" pattern, print a warning message.
* If the position is not one of the three categories (Guard, Forward, Center), print a warning message.
* If the class is not one of the five categories (Freshman, Sophomore, Junior, Senior, Fifth), print a warning message. 

```{r}
validate_player <- function(x){
  if(is.na(x$firstname)) print("The player's first name is missing.")
  if(is.na(x$lastname)) print("The player's last name is missing.")
  if(is.na(x$jersey)) print("The player's jersey information is missing.")
  if(is.na(x$height)) print("The player's height information is missing.")
  if(is.na(x$position)) print("The player's position information is missing.")
  if(is.na(x$class)) print("The player's class information is missing.")
  
  
  if(!grepl("^\\d+-\\d+$", x$height)) # grepl() is searching for matches
    print("The player's height does not follow the 'feet-inches' pattern.")
  if(!str_to_title(x$position) %in% c("Guard", "Forward", "Center")) 
    print("The player's position information is invalid.")
  if(!str_to_title(x$class) %in% c("Freshman", "Sophomore", "Junior", "Senior", "Fifth")) 
    print("The player's class information is invalid.")
}
```



## Create Staff Class

### Constructor Function

```{r}

new_staff = function(x){
  validate_staff(x)
  structure(
    list(name = x$name,
         role = x$role,
         role_with_article = article_selector(x$role) 
         ),
    class = "staff"
  )
}

```

### Helper Function

Choose appropriate article for the role information. 

```{r}
article_selector <- function(role) {
 title <- switch(
   role,
   "head coach" = "the Head Coach",
   "associate head coach" = "the Associate Head Coach",
   "assistant coach" = "an Assistant Coach",
   "a staff member"
  )
 return(title)
}

```


### Validator Function

* if name or role is missing or not character type, print warning message. 

```{r}
validate_staff <- function(x){
  if(is.na(x$name) || !is.character(x$name)) 
    print("The staff's name is not valid")
  if(is.na(x$role)|| !is.character(x$role)) 
    print("The staff's role information is not valid")
}
```


## Create Spectator Class


```{r}

new_spectator = function(x){
  structure(
    list(name = x$name),
    class = "spectator"
  )
}

```

## Generic and Methods

* Define the generic `print_profile` and the methods.

```{r}
print_profile = function(x){
  UseMethod("print_profile")
}

print_profile.player = function(x){
  print(paste0(x$firstname, " ", x$lastname, " is a player on the U of I Women's Basketball Team. Her jersey number is ", x$jersey, ". ",  x$firstname, " is a student in her ", x$studentclass, " year. She is ", x$height_inches, " tall (", x$heightcm," cm). Her position is ", x$position, "." 
               )
        )
}

print_profile.staff = function(x){
  print(paste0(x$name, " is ", x$role_with_article, 
               " of the U of I Women's Basketball Team." ))
}

print_profile.default = function(x){
  print(paste0(x$name, " is neither a player nor a staff member."))
}
```


## Test

```{r, error=TRUE}
# Player

Mckenzie <- new_player(x = list(
  firstname = "Adalia",
  lastname = "Mckenzie",
  jersey = "24",
  height = "5-10",
  position = "guard",
  class = "senior"
)
)

### Incorrect Usage
Bryant <- new_player(x = list(
  firstname = "Genesis",
  lastname = "Bryant",
  jersey = "1",
  height = "5'6''", 
  position = "guard",
  class = "fifth"))
# Corrected
Bryant <- new_player(x = list(
  firstname = "Genesis",
  lastname = "Bryant",
  jersey = "1",
  height = "5-6", 
  position = "guard",
  class = "fifth"))


# Staff

Green <- new_staff(x = list(
  name = "Shauna Green", 
  role = "head coach"
  )
)

Solomon <- new_staff(x = list(
  name = "Maya Solomon", 
  role = "director of basketball operations"
  )
)

# Spectator

Jia <- new_spectator(x = list(
  name = "Weijia Jia"
  ))
print_profile(Mckenzie)
print_profile(Bryant)
print_profile(Green)
print_profile(Solomon)
print_profile(Jia)
```
